---
title: "blblm vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blblm)
library(bench)
```

This R package is designed to asssist with bootstrapping and linear regression as well as
generalized linear models, by integrating the two in simple functions. It allows the user to 
easily perform these calculations, without designing the functions themselves. Furthermore, 
the user has the ability to use parallel computing to speed up the processing of the 
bootstrap samples. Parallel computing can speed up the process by 4 times in this situation. 
Additionally, the package contains functions that find the average cofficients of the variables
as well as their standard errors. Confidence intervals and predictions can also be done with this 
package. Examples of how to use the package are shown below. 

```{r}
#non parallel lm 

#blblm function was modified  using rsample package to improve speed.
l<-blblm(wt~mpg,mtcars, 1000)


#coeff and sigma functions were rewritten to accept slightly different format.
coeff.blb(l)
se.blb(l)


#predict was modified and confint was rewritten to accept new format of bootstrap objects
predicts.blb(l, data.frame(wt = c(2.5, 3), mpg=c(20,30)), confidence=TRUE)
confints.blb(l, level=0.9)
```

```{r}
#parallel lm

#parallel function is much faster than the standard blblm function. It was done using parSapply.
l<-parr.blblm(wt~mpg,mtcars,1000,4)

#coeff ans sigma functions work the same with parr.blblm
coeff.blb(l)
se.blb(l)

#predict and confint function work the same with parr.blblm
predicts.blb(l, data.frame(wt = c(2.5, 3), mpg=c(20,30)), confidence=TRUE)
confints.blb(l, level=0.9)
```



```{r}
#non parallel glm

#this function is very similar to blblm but modified for the glm interface
df<-data.frame(Titanic)
l<-blbglm(Survived~Class+Sex, binomial, df,1000)

#coeff, se, predict functions interact the same
coeff.blb(l)
se.blb(l)
confints.blb(l, level=0.9)
```


```{r}
#parallel glm


#Modified the parr.blblm function to accept GLM inputs
l<-parr.blbglm(Survived~Class+Sex, binomial, df,1000, 4)
coeff.blb(l)
se.blb(l)
confints.blb(l, level=0.9)
```



```{r}
#Our blblm function is about 8 seconds faster than the blblm from the base package
result <- bench::mark(
  l<-blblm(wt~mpg,mtcars, 10000),
  relative = FALSE
)
result
```

```{r}
#Our parallel function takes about 5 seconds for a bootstrap of 10000,
#This makes it approximately 4 times faster than the blblm function given to us.
result <- bench::mark(
  l<-parr.blblm(wt~mpg,mtcars,10000,4),
  relative = FALSE
)
result
```

```{r}
#Normal blglm takes 15 seconds here for 1000 bootstraps

df<-data.frame(Titanic)
result <- bench::mark(
  l<-blbglm(Survived~Class+Sex, binomial, df,1000),
  relative = FALSE
)
result
```

```{r}
#Parallel blglm takes 2 seconds here for 1000 bootstraps, and is faster with a bigger sample too 

df<-data.frame(Titanic)
result <- bench::mark(
  l<-parr.blbglm(Survived~Class+Sex, binomial, df,1000, 4),
  relative = FALSE
)
result
```


