---
title: "blblm vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blblm)
```

This R package is designed to asssist with bootstrapping and linear regression as well as
generalized linear models, by integrating the two in simple functions. It allows the user to 
easily perform these calculations, without designing the functions themselves. Furthermore, 
the user has the ability to use parallel computing to speed up the processing of the 
bootstrap samples. Parallel computing can speed up the process by 4 times in this situation. 
Additionally, the package contains functions that find the average cofficients of the variables
as well as their standard errors. Confidence intervals and predictions can also be done with this 
package. Examples of how to use the package are shown below. 


```{r}
#non parallel lm 
l<-blblm(wt~mpg,mtcars, 1000)
coeff.blb(l)
se.blb(l)
predicts.blb(l, data.frame(wt = c(2.5, 3), mpg=c(20,30)), confidence=TRUE)
confints.blb(l, level=0.9)



#parallel lm
l<-parr.blblm(wt~mpg,mtcars,1000,4)
coeff.blb(l)
se.blb(l)
predicts.blb(l, data.frame(wt = c(2.5, 3), mpg=c(20,30)), confidence=TRUE)
confints.blb(l, level=0.9)

#non parallel glm
df<-data.frame(Titanic)
l<-blbglm(Survived~Class+Sex, binomial, df,1000)
coeff.blb(l)
se.blb(l)
confints.blb(l, level=0.9)


#parallel glm
l<-parr.blbglm(Survived~Class+Sex, binomial, df,1000, 4)
coeff.blb(l)
se.blb(l)
confints.blb(l, level=0.9)
```
